\textbf{Computational Fuzzy Extractors}

### 2013-03-04 trunk/CompFuzzExt.tex
Run through of paper fixes, not done proofs

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$. $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then a randomness extractor.  In the next section, we show this paradigm is difficult to realize.

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.  These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

@@

Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows. Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.  Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y$ with high probability.  In particular, $\Pr_{y\in Y} [y'\leftarrow B_t(y) \wedge \rec(y', \sketch(y)) = y ]\geq 1-\epsilon$.  This means we can construct a set $C$ out of the points in the support of $Y$.  Then $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  
%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$. \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

>>>>

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. %We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$. $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  In this paper, we ask whether a smaller entropy loss can be achieved by considering a fuzzy extractor with a computational security requirement.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then apply a randomness extractor~(extractors convert distributions with high computational entropy to pseudorandom).  In the next section, we show this paradigm is difficult to realize.

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the size of a ball in the metric space.  
%These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

@@

%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows. Consider a function $\rec$ where $\rec (w', \sketch(w)) = w$ when $\dis(w, w')\leq t$.  When we consider the distribution $W$, to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ with $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $Y| \sketch(W)$ is computationally indistinguishable from $W | \sketch(W)$.  Since we know that $\rec$ succeeds with high probability, this means $\rec$ must succeed on $Y, \sketch(W)$ with high probability.  In particular, $\Pr [s\leftarrow \sketch(W) \wedge y\leftarrow Y_s\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y ]\geq 1-\epsilon$.  This means we can construct a large set $C$ from the support of $Y$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.  
%\lnote{this intuition is confusing, esp. given notational inconsistencies of all the capital letters with what comes above and below}
To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{sam}, t)$-\emph{neighborhood efficently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that for all $t'\leq t$, $\sample (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution over space $\mathcal{M}$ with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.
